Classless Java

### 2015-11-16 paper/sections/Translation.tex
proof in appendix.

\noindent$[\![\mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs \oC \methods \cC ]\!] =
\emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC
\methods\ \methods' \cC
$\\*${}_{}$\tab
where  $\valid(\C_0)$,\Q@of@$\notin\dom(\methods)$ and $\methods'=\ofMethod(\C_0) \ \otherMethod(\C_0,\methods)$.\\*

@@

\subsection{$\ofMethod$}${}_{}$\\*
We now formally define $\ofMethod$, the function that generates the method \QM{of}, that behaves like a factory. To avoid boring digressions about well known ways to find unique names, for the sake of this formalization we assume that no-args methods do not start with underscore, and we prefix method names with underscore to obtain valid  parameter names.\\*
\noindent$\begin{array}{l}
\ofMethod(\C_0) = \
 \QM{static}\ C_0\ \QM{of} \oR \C_1\ \QM_\m_1\QM,\ldots \C_n\ \QM_\m_n\cR\
\QM{\{}
\QM{return new}\ C_0 \oR\cR\ \QM{\{} \\
\tab\tab\tab\tab\tab\tab\tab C_1\ \m_1 = \QM_\m_1\QM;\ldots \C_n\ \m_n = \QM_\m_n\QM; \\
\tab\tab\tab\tab\tab\tab\tab
\C_1\ \m_1\oR\cR\ \QM{\{return }\ \m_1\QM{;\}}\ \ldots
\C_n\ \m_n\oR\cR\ \QM{\{return }\ \m_n\QM{;\}}\\
\tab\tab\tab\tab\tab\tab\tab\withMethod(\C_1,\m_1,\C_0,\es_1)\ldots\withMethod(\C_n,\m_n,\C_0,\es_n)\\
\tab\tab\tab\tab\tab\tab\tab\setterMethod(\C_1,\m_1,\C_0)\ldots\setterMethod(\C_n,\m_n,\C_0)\\
%\tab\tab\tab\tab\tab\tab\tab\cloneMethod(\C_0,\es)\\
\tab\tab\tab\tab\tab\tab\tab\withMethod(\C_0)\\
\tab\tab\tab\tab\tab\tab\QM{\};\}} \\
\end{array}$
\\*
with $\fieldsFunc(\C_0)=\C_1\ \m_1\QM{();},\ldots \C_n\ \m_n\QM{();}$,\\*
and $\es_i=\m_1\QM,\ldots\QM, \m_{i-1}\QM,\QM{_val,}\m_{i+1}\QM,\ldots\QM, \m_n$\\*
%and $\es=\m_1\QM,\ldots\QM, \m_n$\\*

@@

\haoyuan{method name of setter?}

@@

\noindent\textbf{LEMMA. }
If $\II_0$ OK, then $[\![\II_0]\!]$ OK.
\begin{proof}
First assume that $\II_0$ is of form $$\mixinAnn\ \QM{interface}\ C_0\ \QM{extends}\ \overline{C}\ \oC \methods\ \cC$$
By the rule \rn{t-Invk} in Figure~\ref{ET}, we divide it into two parts.

\noindent\textbf{Part I.} For each default or static method in the domain of $[\![\II_0]\!]$, the type of the return value is compatible with the method's return type.

Since $\II_0$ OK, all the existing default and static methods are well typed in $[\![\II_0]\!]$, except for the new method \QM{of}. It suffices to prove that it still holds for $\ofMethod(C_0)$.

By the definition of $\ofMethod(C_0)$, the return value is an object $$\QM{return new}\ C_0 \oR\cR\ \QM{\{}...\ \QM{\}}$$
To prove it is of type $C_0$, we use the typing rule \rn{t-Obj}.
\begin{itemize}
\item For field typing,
\[\Gamma(\QM_ m_i)=C_i\subtype C_i\]
\item For method typing of getters,
\[\Gamma, m_i:C_i, \QM{this}:C_0, \Gamma^{\mh_i}\vdash m_i\in C_i=C^{\mh_i}\]
\item For method typing of nonempty \QM{with-} methods, by \rn{t-StaticInvk}, \haoyuan{how to do typing for the generated method itself?}
\[\Gamma, \overline{m_i:C_i}, \QM{this}:C_0, \es_i:\overline{C}_i, \Gamma^{\mh_i}\vdash C_0\QM{.of}\oR\es_i\cR\in C_0=C^{\mh_i}\]
\item For method typing of nonempty setter methods, \haoyuan{what about the \QM{with} method?}
\[\Gamma, \QM{this}:C_0, \Gamma^{\mh_i}\vdash\QM{this}\in C_0=C^{\mh_i}\]
\item To prove that $\forall i$, $\mh_i\subtype\mBody(m^{\mh_i}, C_0)$,
 \begin{itemize}
 \item For getters, \[C_i\ m_i\oR\cR\QM; \in \fieldsFunc(C_0) \Rightarrow C_i\ m_i\oR\cR\QM; \in \dom(C_0)\]
 \item For nonempty \QM{with-} methods,
  \[\begin{array}{l}
  \mBody(\QM{with#}\m_i,C_0) \mbox{ is of form }\mh\QM; \\ \valid(C_0)
  \end{array}\Rightarrow \isWith\Rightarrow C_0\subtype\mBody(m^{\mh_i}, C_0)\]
 \item For nonempty setters,
  \[\begin{array}{l}
  \mBody(\m_i,C_0) \mbox{ is of form }\mh\QM; \\ \valid(C_0)
  \end{array}\Rightarrow \isSetter\Rightarrow C_0\subtype\mBody(m^{\mh_i}, C_0)\]
 \end{itemize}
\item To prove that such a created object indeed implements all the abstract methods in $\dom(C_0)$, we simply refer to $\valid(C_0)$, since it guarantees each abstract method $\method$ to satisfy $\isField$, $\isWith$ or $\isSetter$. But that object includes all implementations for those cases, hence it is of type $C_0$ by \rn{t-Obj}.
\end{itemize}

\noindent\textbf{Part II.} Next we check $\dom(C_0)=\dom(C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)\cup\dom(\methods')$.

\end{proof}

>>>>

\noindent$[\![\mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC ]\!] =
\emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC
\methods\ \methods' \cC
$\\*${}_{}$\tab
where  $\valid(\C_0)$,\Q@of@$\notin\dom(\methods)$ and $\methods'=\ofMethod(\C_0) \ \otherMethod(\C_0,\methods)$.\\*

@@

\subsection{$\ofMethod$}${}_{}$\\*
We now formally define $\ofMethod$, the function that generates the method \QM{of}, that behaves like a factory. To avoid boring digressions about well known ways to find unique names, for the sake of this formalization we assume that no-args methods do not start with underscore, and we prefix method names with underscore to obtain valid  parameter names.\\*
\noindent$\begin{array}{l}
\ofMethod(\C_0) = \
 \QM{static}\ \C_0\ \QM{of} \oR \C_1\ \QM_\m_1\QM,\ldots \C_n\ \QM_\m_n\cR\
\QM{\{}
\QM{return new}\ \C_0 \oR\cR\ \QM{\{} \\
\tab\tab\tab\tab\tab\tab\tab \C_1\ \m_1 = \QM_\m_1\QM;\ldots \C_n\ \m_n = \QM_\m_n\QM; \\
\tab\tab\tab\tab\tab\tab\tab
\C_1\ \m_1\oR\cR\ \QM{\{return }\ \m_1\QM{;\}}\ \ldots
\C_n\ \m_n\oR\cR\ \QM{\{return }\ \m_n\QM{;\}}\\
\tab\tab\tab\tab\tab\tab\tab\withMethod(\C_1,\m_1,\C_0,\es_1)\ldots\withMethod(\C_n,\m_n,\C_0,\es_n)\\
\tab\tab\tab\tab\tab\tab\tab\setterMethod(\C_1,\m_1,\C_0)\ldots\setterMethod(\C_n,\m_n,\C_0)\\
%\tab\tab\tab\tab\tab\tab\tab\cloneMethod(\C_0,\es)\\
\tab\tab\tab\tab\tab\tab\tab\withMethod(\C_0)\\
\tab\tab\tab\tab\tab\tab\QM{\};\}} \\
\end{array}$
\\*
with $\fieldsFunc(\C_0)=\C_1\ \m_1\QM{();},\ldots \C_n\ \m_n\QM{();}$,\\*
and $\es_i=\m_1\QM,\ldots\QM, \m_{i-1}\QM,\QM{_val,}\m_{i+1}\QM,\ldots\QM, \m_n$\\*
%and $\es=\m_1\QM,\ldots\QM, \m_n$\\*
\haoyuan{Should we include the $\withMethod(\C_0)$ in the formalization?}

@@

\haoyuan{method name of setter? $m$ or $\_m$?}

@@

To prove the theorem we introduce two lemmas below. The complete proof is available in Appendix \ref{subsec:proof1}, \ref{subsec:proof2} and \ref{subsec:proof3}.\\

\noindent\textbf{LEMMA 1. }
If $\II_0$ satisfies $\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)$, then $[\![\II_0]\!]$ satisfies $\dom'(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)\cup\dom(\methods')$.\\

\noindent\textbf{LEMMA 2. }
If $\II_0$ OK, then $[\![\II_0]\!]$ OK.
